Two-Phase Commit Using Blockchain

### 2022-06-04 paper/paper.tex
Add citation and update diagram.

\documentclass[11pt,conference]{IEEEtran}
\IEEEoverridecommandlockouts
\usepackage[sort,nocompress]{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage[htt]{hyphenat}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}

@@

\section{Implementation}
In this section we first describe the implementation of our overall system. Then, we illustrate the implementation of individual components. The source code of our implementation is available at licensed under GNU Lesser General Public License. Our implementation depends on the following libraries: ganache, truffle, sqlite3, grpc/grpc-js, grpc/proto-loader, web3, web3-eth-contract, absl, rule\_nodejs, gflags, glog, openssl, threadpool \cite{Shoshany2021_ThreadPool}, lmdb, and lmdbxx.

\subsection{Environment}
We implemented the coordinator and the cohorts with about 2800 lines of C++ code. For communications between components, we used gRPC \cite{} and ProtoBuf \cite{}. For providing the extensibility of swapping different database and blockchain implementations, we provided generic interfaces. We tested end-to-end behaviors on a single machine with different processes simulating each component.

\subsubsection{Blockchain}
We wrote our two-phase-commit smart contract with Solidity and developed it with Truffle \cite{}. Truffle provided the development environment for us to compile smart contracts, test it, and deploy it locally for debugging. Once we deployed our smart contract, the coordinator and the cohorts interacted with the contract through a smart contract client library. However, we didn’t find a proper C++ smart contract client library to use, so we used a JavaScript library (web.js[ref]) instead and added an additional gRPC layer to translate to C++.

>>>>

\documentclass[11pt,conference]{IEEEtran}
\IEEEoverridecommandlockouts
\usepackage[sort,nocompress]{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{textcomp}
\usepackage{url}
\usepackage{xcolor}
\usepackage[htt]{hyphenat}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}

@@

\section{Implementation}
In this section we first describe the implementation of our overall system. Then, we illustrate the implementation of individual components. The source code of our implementation is available at licensed under GNU Lesser General Public License. Our implementation depends on the following libraries: truffle \cite{github_truffle}, gganacheanache \cite{github_ganache}, sqlite3 \cite{github_sqlite3}, grpc \cite{github_grpc}, web3 \cite{github_web3}, abseil-cpp \cite{github_absl}, rule\_nodejs \cite{github_rulejs}, gflags \cite{github_gflags}, glog \cite{github_glog}, openssl \cite{github_openssl}, threadpool \cite{Shoshany2021_ThreadPool}, lmdb \cite{github_lmdb}, and lmdbxx \cite{github_lmdbxx}.

\subsection{Environment}
We implemented the coordinator and the cohorts with about 2800 lines of C++ code. For communications between components, we used gRPC \cite{github_grpc} and ProtoBuf \cite{github_proto}. For providing the extensibility of swapping different database and blockchain implementations, we provided generic interfaces. We tested end-to-end behaviors on a single machine with different processes simulating each component.

\subsubsection{Blockchain}
We wrote our two-phase-commit smart contract with Solidity and developed it with Truffle \cite{github_truffle}. Truffle provided the development environment for us to compile smart contracts, test it, and deploy it locally for debugging. Once we deployed our smart contract, the coordinator and the cohorts interacted with the contract through a smart contract client library. However, we didn’t find a proper C++ smart contract client library to use, so we used a JavaScript library (web.js[ref]) instead and added an additional gRPC layer to translate to C++.
